Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-05-18 supp_mat_complexity_selection.Rmd
exploring alternative models

# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
# also, using 'refit.smooth = T' also generated some very skewed distributions
# the recipe below provided the most sensible estimates for my data
gradient.calc <- function(mod, phenotype, covariates = NULL) {
  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
                refit.smooth = T, # F
                n.boot = 1000,
                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
                standardized = T)
}

@@

## CONTROL PLANTS ----
gamm_full.control <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots + 
                                  gall_individuals:Density_per_100_shoots,
                                data = control_df)
summary(gamm_full.control$gam)
summary(gamm_full.control$mer)

@@

AIC(gamm_full.control$mer, gamm_red.control$mer)

## TREATMENT PLANTS ----
gamm_full.treatment <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots + 
                                  gall_individuals:Density_per_100_shoots,
                                data = treatment_df)
summary(gamm_full.treatment$gam)
summary(gamm_full.treatment$mer)

@@

AIC(gamm_full.treatment$mer, gamm_red.treatment$mer)
```
Parametric bootstrapping: Currently reported results

@@

Permutation: qualtiative results are consistent with parametric bootstrapping. Exceptions include: in the simple food-web, there is no evidence of non-linear selection for gall density or gall individuals. In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE}
## Estimate directional, nonlinear, and correlational selection gradients
sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
                                 phenotype = "Gall_Height_mm", 
                                 covariates = c("gall_individuals","Density_per_100_shoots"))
sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                   phenotype = "Gall_Height_mm", 
                                   covariates = c("gall_individuals","Density_per_100_shoots"))
sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                        phenotype = "gall_individuals", 
                                        covariates = c("Gall_Height_mm","Density_per_100_shoots"))
sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                          phenotype = "gall_individuals", 
                                          covariates = c("Gall_Height_mm","Density_per_100_shoots"))
sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                    phenotype = "Density_per_100_shoots", 
                                    covariates = c("gall_individuals","Gall_Height_mm"))
sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                      phenotype = "Density_per_100_shoots", 
                                      covariates = c("gall_individuals","Gall_Height_mm"))
sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("Gall_Height_mm", "gall_individuals"),
                                               covariates = c("Density_per_100_shoots"))
sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("Gall_Height_mm", "gall_individuals"),
                                                 covariates = c("Density_per_100_shoots"))
sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("Gall_Height_mm", "Density_per_100_shoots"),
                                               covariates = c("gall_individuals"))
sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("Gall_Height_mm","Density_per_100_shoots"),
                                                 covariates = c("gall_individuals"))
sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                                  phenotype = c("Density_per_100_shoots", "gall_individuals"),
                                                  covariates = c("Gall_Height_mm"))
sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                    phenotype = c("Density_per_100_shoots", "gall_individuals"),
                                                    covariates = c("Gall_Height_mm"))

## Summarise the results
sg.summary <- bind_rows(
          data.frame(sg.size_control$ests, #round(,3), 
                     gradients = rownames(sg.size_control$ests),
                     treatment = "Complex"),
          data.frame(sg.size_treatment$ests, #round(,3), 
                     gradients = rownames(sg.size_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.individuals_control$ests, #round(,3), 
                     gradients = rownames(sg.individuals_control$ests),
                     treatment = "Complex"),
          data.frame(sg.individuals_treatment$ests, #round(,3), 
                     gradients = rownames(sg.individuals_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.density_control$ests, #round(,3), 
                     gradients = rownames(sg.density_control$ests),
                     treatment = "Complex"),
          data.frame(sg.density_treatment$ests, #round(,3), 
                     gradients = rownames(sg.density_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.size.x.individuals_control$ests, #round(,3), 
                     gradients = rownames(sg.size.x.individuals_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.size.x.individuals_treatment$ests, #round(,3), 
                     gradients = rownames(sg.size.x.individuals_treatment$ests),
                     treatment = "Simple")[5,],
          data.frame(sg.size.x.density_control$ests, #round(,3), 
                     gradients = rownames(sg.size.x.density_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.size.x.density_treatment$ests, #round(,3), 
                     gradients = rownames(sg.size.x.density_treatment$ests),
                     treatment = "Simple")[5,],
          data.frame(sg.density.x.individuals_control$ests, #round(,3), 
                     gradients = rownames(sg.density.x.individuals_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.density.x.individuals_treatment$ests, #round(,3), 
                     gradients = rownames(sg.density.x.individuals_treatment$ests),
                     treatment = "Simple")[5,])

@@

```{r}
hist(as.numeric(sg.density_control$boot[ ,1]))
## BOOTSTRAPPED INTERVALS ----
bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,1]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,2]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  # correlational
  data.frame(Bootstrap_Estimates = as.numeric(sg.size.x.individuals_control$boot[ ,5]), Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size.x.individuals_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
    data.frame(Bootstrap_Estimates = sg.size.x.density_control$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size.x.density_treatment$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density.x.individuals_control$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density.x.individuals_treatment$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
)

@@

@@

## 1-DIMENSIONAL
uni_size <- bind_rows(mutate(get_insect_FL.df(fl.size_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.size_treatment), Treatment = "Simple")) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Mean fitness") +
  xlab("Mean gall size") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors) +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))

uni_clutch <- bind_rows(mutate(get_insect_FL.df(fl.individuals_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.individuals_treatment), Treatment = "Simple")) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Mean fitness") +
  xlab("Mean clutch size") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors) +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))

uni_pref <- bind_rows(mutate(get_insect_FL.df(fl.density_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.density_treatment), Treatment = "Simple")) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Mean fitness") +
  xlab("Mean female preference") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors) +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))

@@

## 2-DIMENSIONAL
clutch.x.size_2d <- bind_rows(
  mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
  mutate(get_insect_FL.df(fl.individuals.x.size_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Mean fitness") +
  xlab("Mean gall size") +
  ylab("Mean clutch size")

>>>>

# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
# also, using 'refit.smooth = T' also generated some very skewed distributions
# the recipe below provided the most sensible estimates for my data
gradient.calc <- function(mod, phenotype, covariates = NULL) {
  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
                refit.smooth = F,
                n.boot = 1000,
                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
                standardized = T)
}

@@

## CONTROL PLANTS ----
gamm_red.control <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots + 
                                  gall_individuals:Density_per_100_shoots,
                                data = control_df)
summary(gamm_full.control$gam)
summary(gamm_full.control$mer)

@@

gamm_red.control.noG <- gamm4(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots),
                                  random = ~(1|Plant_Position/Gall_Number), 
                                  family = binomial(link = logit),
                                data = control_df)
summary(gamm_red.control.noG$gam)
summary(gamm_red.control.noG$mer)

glmm_full.control <- gamm.model(gall_survival ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots +
                                  gall_individuals:Density_per_100_shoots,
                                data = control_df)
summary(glmm_full.control$gam)
summary(glmm_full.control$mer)

glmm_red.control <- gamm.model(gall_survival ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
                                data = control_df)
summary(glmm_red.control$gam)
summary(glmm_red.control$mer)

lmm_red.control <- gamm4(gall_survival ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
                           random = ~(1|Plant_Position/Gall_Number),
                                data = control_df, family=gaussian())
summary(lmm_red.control$gam)
summary(lmm_red.control$mer)

AIC(gamm_full.control$mer, gamm_red.control$mer, gamm_red.control.noG$mer, glmm_full.control$mer, glmm_red.control$mer, lmm_red.control$mer)

## TREATMENT PLANTS ----
gamm_red.treatment <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots + 
                                  gall_individuals:Density_per_100_shoots,
                                data = treatment_df)
summary(gamm_full.treatment$gam)
summary(gamm_full.treatment$mer)

@@

gamm_red.treatment.noG <- gamm4(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots),
                                  random = ~(1|Plant_Position/Gall_Number), 
                                  family = binomial(link = logit),
                                data = treatment_df)
summary(gamm_red.treatment.noG$gam)
summary(gamm_red.treatment.noG$mer)

glmm_full.treatment <- gamm.model(gall_survival ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots +
                                  gall_individuals:Density_per_100_shoots,
                                data = treatment_df)
summary(glmm_full.treatment$gam)
summary(glmm_full.treatment$mer)

glmm_red.treatment <- gamm.model(gall_survival ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
                                data = treatment_df)
summary(glmm_red.treatment$gam)
summary(glmm_red.treatment$mer)

lmm_red.treatment <- gamm4(gall_survival ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
                           random = ~(1|Plant_Position/Gall_Number),
                                data = treatment_df, family=gaussian())
summary(lmm_red.treatment$gam)
summary(lmm_red.treatment$mer)

AIC(gamm_full.treatment$mer, gamm_red.treatment$mer, gamm_red.treatment.noG$mer, glmm_full.treatment$mer, glmm_red.treatment$mer, lmm_red.treatment$mer)

## Linear mixed-models
lmm_full.control <- lmer(gall_survival/0.45 ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots +
                                  gall_individuals:Density_per_100_shoots +
                           (1|Genotype/Plant_Position/Gall_Number),
                                data = control_df)
summary(lmm_full.control)
car::Anova(lmm_full.control, test="F")
visreg::visreg(lmm_full.control)

lmm_full.treatment <- lmer(gall_survival/0.6 ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots +
                                  gall_individuals:Density_per_100_shoots +
                             (1|Genotype/Plant_Position/Gall_Number),
                                data = treatment_df)
summary(lmm_full.treatment)
car::Anova(lmm_full.treatment, test="F")

lmm_red.treatment <- lmer(gall_survival/0.6 ~ 
                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
                              (1|Genotype/Plant_Position/Gall_Number),
                                data = treatment_df)
summary(lmm_red.treatment)
car::Anova(lmm_red.treatment, test="F")
visreg::visreg(lmm_red.treatment)

AIC(lmm_full.treatment, lmm_red.treatment)

gall_selection.df$relative.fit <- with(gall_selection.df, ifelse(Treatment.focus=="Control", gall_survival/0.45, gall_survival/0.6))

lmm_full <- lmer(relative.fit ~ poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) + 
                                poly(Gall_Height_mm,2):Treatment.focus + 
                                poly(gall_individuals,2):Treatment.focus + 
                                poly(Density_per_100_shoots,2):Treatment.focus +
                                (1|Genotype/Plant_Position/Gall_Number),
                                data = gall_selection.df)
summary(lmm_full)
car::Anova(lmm_full, test="F")
visreg::visreg(lmm_full, xvar="Gall_Height_mm", by="Treatment.focus")
visreg::visreg(lmm_full, xvar="gall_individuals", by="Treatment.focus")
visreg::visreg(lmm_full, xvar="Density_per_100_shoots", by="Treatment.focus")
```
Parametric bootstrapping: Currently reported results

@@

Permutation: qualtiative results are consistent with parametric bootstrapping. Exceptions include: in the simple food-web, there is no evidence of non-linear selection for gall density or gall individuals. In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE}

## Estimate directional, nonlinear, and correlational selection gradients
sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
                                 phenotype = "Gall_Height_mm", 
                                 covariates = c("gall_individuals","Density_per_100_shoots"))
sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                   phenotype = "Gall_Height_mm", 
                                   covariates = c("gall_individuals","Density_per_100_shoots"))
sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                        phenotype = "gall_individuals", 
                                        covariates = c("Gall_Height_mm","Density_per_100_shoots"))
sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                          phenotype = "gall_individuals", 
                                          covariates = c("Gall_Height_mm","Density_per_100_shoots"))
sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                    phenotype = "Density_per_100_shoots", 
                                    covariates = c("gall_individuals","Gall_Height_mm"))
sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                      phenotype = "Density_per_100_shoots", 
                                      covariates = c("gall_individuals","Gall_Height_mm"))
sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("Gall_Height_mm", "gall_individuals"),
                                               covariates = c("Density_per_100_shoots"))
sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("Gall_Height_mm", "gall_individuals"),
                                                 covariates = c("Density_per_100_shoots"))
sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("Gall_Height_mm", "Density_per_100_shoots"),
                                               covariates = c("gall_individuals"))
sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("Gall_Height_mm","Density_per_100_shoots"),
                                                 covariates = c("gall_individuals"))
sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                                  phenotype = c("Density_per_100_shoots", "gall_individuals"),
                                                  covariates = c("Gall_Height_mm"))
sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                    phenotype = c("Density_per_100_shoots", "gall_individuals"),
                                                    covariates = c("Gall_Height_mm"))

## Summarise the results
sg.summary <- bind_rows(
          data.frame(sg.size_control$ests,  
                     gradients = rownames(sg.size_control$ests),
                     treatment = "Complex"),
          data.frame(sg.size_treatment$ests, 
                     gradients = rownames(sg.size_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.individuals_control$ests,  
                     gradients = rownames(sg.individuals_control$ests),
                     treatment = "Complex"),
          data.frame(sg.individuals_treatment$ests,  
                     gradients = rownames(sg.individuals_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.density_control$ests, 
                     gradients = rownames(sg.density_control$ests),
                     treatment = "Complex"),
          data.frame(sg.density_treatment$ests, 
                     gradients = rownames(sg.density_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.size.x.individuals_control$ests,  
                     gradients = rownames(sg.size.x.individuals_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.size.x.individuals_treatment$ests,  
                     gradients = rownames(sg.size.x.individuals_treatment$ests),
                     treatment = "Simple")[5,],
          data.frame(sg.size.x.density_control$ests,  
                     gradients = rownames(sg.size.x.density_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.size.x.density_treatment$ests,  
                     gradients = rownames(sg.size.x.density_treatment$ests),
                     treatment = "Simple")[5,],
          data.frame(sg.density.x.individuals_control$ests, 
                     gradients = rownames(sg.density.x.individuals_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.density.x.individuals_treatment$ests, 
                     gradients = rownames(sg.density.x.individuals_treatment$ests),
                     treatment = "Simple")[5,])

@@

```{r}

## BOOTSTRAPPED INTERVALS ----
bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "Oviposition preference", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "Oviposition preference", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  # correlational
  data.frame(Bootstrap_Estimates = sg.size.x.individuals_control$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size.x.individuals_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
    data.frame(Bootstrap_Estimates = sg.size.x.density_control$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size.x.density_treatment$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density.x.individuals_control$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density.x.individuals_treatment$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
)

@@

Compare bootstrapped replicates across treatments, rather than comparing to zero.
```{r}
bootstrap_df %>%
  filter(Phenotype == "Gall size", Selection_Type == "Beta") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

bootstrap_df %>%
  filter(Phenotype == "Gall size", Selection_Type == "Gamma") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

bootstrap_df %>%
  filter(Phenotype == "Clutch size", Selection_Type == "Beta") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

bootstrap_df %>%
  filter(Phenotype == "Clutch size", Selection_Type == "Gamma") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

bootstrap_df %>%
  filter(Phenotype == "Oviposition preference", Selection_Type == "Beta") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

bootstrap_df %>%
  filter(Phenotype == "Oviposition preference", Selection_Type == "Gamma") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

bootstrap_df %>%
  filter(Phenotype == "Size,Clutch", Selection_Type == "Correlational") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient > 0)/1000) # flipped sign

bootstrap_df %>%
  filter(Phenotype == "Size,Pref.", Selection_Type == "Correlational") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient > 0)/1000) # flipped sign

bootstrap_df %>%
  filter(Phenotype == "Pref.,Clutch", Selection_Type == "Correlational") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)
```

@@

## 1-DIMENSIONAL
uni_size <- bind_rows(mutate(get_insect_FL.df(fl.size_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.size_treatment), Treatment = "Simple")) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Population mean fitness") +
  xlab("Mean gall size\n(mm)") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors) +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))

uni_clutch <- bind_rows(mutate(get_insect_FL.df(fl.individuals_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.individuals_treatment), Treatment = "Simple")) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Population mean fitness") +
  xlab("Mean clutch size\n(no. of larva)") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors) +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))

uni_pref <- bind_rows(mutate(get_insect_FL.df(fl.density_control), Treatment = "Complex"),
          mutate(get_insect_FL.df(fl.density_treatment), Treatment = "Simple")) %>%
  ggplot(.) +
  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
  ylab("Population mean fitness") +
  xlab("Mean oviposition preference\n(larva per 100 shoots)") +
  scale_color_manual(values = treatmeant_colors) +
  scale_fill_manual(values = treatmeant_colors) +
  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))

@@

## 2-DIMENSIONAL
clutch.x.size_2d <- bind_rows(
  mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
  mutate(get_insect_FL.df(fl.individuals.x.size_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Population\nmean fitness") +
  xlab("Mean gall size (mm)") +
  ylab("Mean clutch size (no. larva)")

size.x.pref_2d <- bind_rows(
  mutate(get_insect_FL.df(fl.size.x.density_treatment), Treatment="Simple"),
  mutate(get_insect_FL.df(fl.size.x.density_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var2, y=Var1, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Population\nmean fitness") +
  xlab("Mean gall size (mm)") +
  ylab("Mean oviposition preference (no. larva per 100 shoots)")
